---
title: "P8150 HW1"
author: "Ziwei Zhao"
date: "2021/9/22"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
```

### Problem 1

Create a data frame df1.

```{r, message = FALSE}
#Set a random seed
set.seed(6789)
#Create a data frame
df1 <- 
  tibble(
    #a random sample of size 10 from a standard Normal distribution
    vec_num = rnorm(10), 
    #a logical vector indicating whether elements of the sample are greater than 0
    vec_log = vec_num > 0,
    #a character vector of length 10
    vec_char = c("AA", "BB", "CC", "DD", "EE", "FF", "GG", "HH", "II", "JJ"),
    #a factor vector of length 10, with 3 different factor “levels”
    vec_fac = factor(
      c("level 1", "level 2", "level 3", "level 3", "level 2", "level 1", "level 1", "level 1", "level 2", "level 3")
    )
  )
#Show the data frame
df1
```

Take the mean of each variable in your data frame.

```{r, message=FALSE, warning=FALSE}
#Take the mean of vec_num
mean(pull(df1, vec_num))
#Take the mean of vec_log
mean(pull(df1, vec_log))
#Take the mean of vec_char
mean(pull(df1, vec_char))
#Take the mean of vec_fac
mean(pull(df1, vec_fac))
```

Means can be calculated for numeric and logical vectors, but cannot be calculated for character and factor vectors.

Then, apply `as.numeric` to the logical, character, and factor variables

```{r, echo=T, results='hide', warning=FALSE}
#for numeric vector
as.numeric(pull(df1, vec_num))
#for logical vector
as.numeric(pull(df1, vec_log))
#for character vector
as.numeric(pull(df1, vec_char))
#for factor vector
as.numeric(pull(df1, vec_fac))
```

Numeric, logical, and factor values can be converted to numeric values by `as.numeric`, but `as.numeric` returns NA for all character values. This means when we try to take the mean, `mean` will not automatically apply `as.numeric` to those values, because factor values can be converted to numeric values by `as.numeric` but `mean` still cannot calculate their mean.

### Problem 2

```{r, message=FALSE}
#Install the package if you haven't done so
#install.packages("palmerpenguins")

#Load the penguins dataset
data("penguins", package = "palmerpenguins")
#The size of the penguins dataset
row <- nrow(penguins)
col <- ncol(penguins)
#The mean flipper length, remove NAs by applying na.omit
mean <- mean(na.omit(pull(penguins, flipper_length_mm)))
```

The data set includes information of penguins' `r names(penguins)`.The data set has `r row` rows and `r col` columns. The mean flipper length is `r mean`mm, which was calculated after removing NAs.

```{r, message=FALSE, warning=FALSE}
#Make the scatterplot
ggplot(penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species)) + geom_point()
#Export the scatterplot
ggsave("scatterplot.pdf")
```

