---
title: "P8150 HW1"
author: "Ziwei Zhao"
date: "2021/9/22"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
```

### Problem 1

Create a data frame df1.

```{r, message = FALSE}
#Set a random seed
set.seed(6789)
#Create a data frame
df1 <- 
  tibble(
    #a random sample of size 10 from a standard Normal distribution
    vec_num = rnorm(10), 
    #a logical vector indicating whether elements of the sample are greater than 0
    vec_log = vec_num > 0,
    #a character vector of length 10
    vec_char = c("AA", "BB", "CC", "DD", "EE", "FF", "GG", "HH", "II", "JJ"),
    #a factor vector of length 10, with 3 different factor “levels”
    vec_fac = factor(
      c("level 1", "level 2", "level 3", "level 3", "level 2", "level 1", "level 1", "level 1", "level 2", "level 3")
    )
  )
#Check the data frame
df1
```

Take the mean of each variable in your data frame.

```{r, message=FALSE}
#Take the mean of vec_num
mean(pull(df1, vec_num))
#Take the mean of vec_log
mean(pull(df1, vec_log))
#Take the mean of vec_char
mean(pull(df1, vec_char))
#Take the mean of vec_fac
mean(pull(df1, vec_fac))
```

Means can be calculated for numeric and logical vectors, but cannot be calculated for character and factor vectors.

Then, apply as.numeric function to the logical, character, and factor variables

```{r, echo=T, results='hide', warning=FALSE}
as.numeric(pull(df1, vec_num))
as.numeric(pull(df1, vec_log))
as.numeric(pull(df1, vec_char))
as.numeric(pull(df1, vec_fac))
```

Numeric, logical, and factor values can be converted to numeric values by as.numeric function, but as.numeric function returns NA for all character values. This means when we try to take the mean, the mean function will not automatically apply as.numeric to those values, because factor values can be converted to numeric values by as.numeric but mean function still cannot calculate their mean.

### Problem 2

```{r, message=FALSE}
#Load the penguins dataset
data("penguins", package = "palmerpenguins")
#The size of the penguins dataset
nrow(penguins)
ncol(penguins)
#The mean flipper length, remove NAs by applying na.omit
mean(na.omit(penguins$flipper_length_mm))
```

The data set includes information about species, island, and sex (factor vectors) of penguins, as well as data of bill length, bill depth, flipper length, body mass, as year (numeric vectors). The data set has 344 rows and 8 columns. The mean flipper length is 200.9mm, which was calculated after removing NAs.

```{r, message=FALSE, warning=FALSE}
#Make the scatterplot
ggplot(penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm, 
           color = species)) + geom_point()
#Export the scatterplot
ggsave("scatterplot.pdf")
```

